\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-30 OaklandSubmission/ex.tex
minor

\subsubsection*{Source language}
Consider the example $w^Tx >b$ from Section~\ref{sec:intro}, where
$w$ and $b$ constitute the server's input (a classifier) and $x$ is
the client's input vector. Figure~\ref{fig:ex-sml} shows the \tool code
for this example. The code first reads the server's (resp. client's) input using
 \ls{input1} (resp. \ls{input2}). It then uses a
\ls{for} loop to compute \ls{acc}, the dot product of \ls{w} and
\ls{x}. Finally, the code outputs the result of comparing \ls{acc}
with \ls{b} only to the client using \ls{output2}.

@@

We can now concretely see the advantages of \tool. Unarguably, it is
easier for a developer to program, and get right, the code in
Figure~\ref{fig:ex-sml}, rather than the code in
Figure~\ref{fig:ex-aby} (as we mentioned in Section~\ref{sec:intro},
other high-level languages are limited in their use of a single,
arithmetic or boolean, crypto back-end). \tool also enables the
programmer to easily modify their code, while the compiler takes care
of efficiency. For example, consider in Figure~\ref{fig:ex-sml} a
change from multiplication to bitwise-or in the \ls{for} loop. It
turns out that once that's the case, it is more efficient to do both
the addition and bitwise-or using boolean circuits (if the addition is
still done using arithmetic, the conversion cost starts to take
over). In \tool, the programmer simply needs to change one operator in
the source code, and the compiler generates efficient code that uses
boolean addition. Whereas, if the programmer was writing ABY
code, she either has to sacrifice performance, or she would have to
revisit many parts of the circuit and change them.

>>>>

\subsubsection*{Source language}
Consider the example $w^Tx >b$ from Section~\ref{sec:intro}, where
$w$ and $b$ constitute the server's input (a classifier) and $x$ is
the client's input vector. Figure~\ref{fig:ex-sml} shows the \tool code
for this example. The code first reads the server's (resp. client's) input using
 \ls{input1} (resp. \ls{input2}). It then uses a
\ls{for} loop to compute \ls{acc}, the inner product of \ls{w} and
\ls{x}. Finally, the code outputs the result of comparing \ls{acc}
with \ls{b} only to the client using \ls{output2}.

@@

We can now concretely see the advantages of \tool. Unarguably, it is
easier for a developer to program and get right the code in
Figure~\ref{fig:ex-sml}, rather than the code in
Figure~\ref{fig:ex-aby}.
% (as we mentioned in Section~\ref{sec:intro},
%other high-level languages are limited in their use of a single,
%arithmetic or boolean, crypto back-end). 
\tool also enables the
programmer to easily modify their code, while the compiler takes care
of efficiency. For example, consider in Figure~\ref{fig:ex-sml} a
change from multiplication to bitwise-or in the \ls{for} loop. It
turns out that once that's the case, it is more efficient to do both
the addition and bitwise-or using boolean circuits (if the addition is
still done using arithmetic, the conversion cost starts to take
over). In \tool, the programmer simply needs to change one operator in
the source code, and the compiler generates efficient code that uses
boolean addition. Whereas, if the programmer was writing ABY
code, she either has to sacrifice performance, or she would have to
revisit many parts of the circuit and change them.
